The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the \revision{OVRO-LWA}

### 2018-05-09 paper.tex
minor revisions

\title{
    The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
    with the Owens Valley \revision{Radio Observatory} Long Wavelength Array
}

@@

We aim for these maps to inform foreground removal strategies in 21-cm cosmology, and we anticipate
additional ancillary science taking advantage of the combination of high fidelity and high
resolution of these maps, including but not limited to studies of the cosmic ray emissivity at low
frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
The maps will be made freely available online at the Legacy Archive for Microwave Background Data
Analysis (LAMBDA)\footnote{\url{https://lambda.gsfc.nasa.gov/}}.

@@

Each map from Figure~\ref{fig:channel-maps} will be made freely available online in Healpix format
\citep{2005ApJ...622..759G} on LAMBDA (\url{https://lambda.gsfc.nasa.gov/}).

>>>>

\title{
    The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\
    with the \revision{OVRO-LWA}
}

@@

We aim for these maps to inform foreground removal strategies in 21-cm cosmology, and we anticipate
additional ancillary science taking advantage of the combination of high fidelity and high
resolution of these maps, including but not limited to studies of the cosmic ray emissivity at low
frequencies, searches for giant radio galaxies, and constraining the galactic synchrotron spectrum.
The maps will be made freely available online at the Legacy Archive for Microwave Background Data
Analysis (LAMBDA)\footnote{
    \url{https://lambda.gsfc.nasa.gov/product/foreground/fg_ovrolwa_radio_maps_info.cfm}
}.

@@

Each map from Figure~\ref{fig:channel-maps} will be made freely available online in Healpix format
\citep{2005ApJ...622..759G} on LAMBDA.
